A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-02-23 sections/Overview.tex
S2.5 examples with more explaination

\jimmy{Some high level description for the structure}
A worklist is structurally a stack with its top element to the right.
$$\begin{aligned}
\text{Algorithmic judgement chain}\qquad&\jg &::=&\quad A \le B \mid e\Lto A \mid e\To_{a} \jg \mid \appInfAlg{A}{e}\\
\text{Algorithmic worklist}\qquad&\Gm &::=&\quad \nil \mid \Gm, a \mid \Gm, \al \mid \Gm, x: A \mid \Gm \Vdash \jg\\
\end{aligned}$$

@@

For example, the top judgment of the following worklist
checks the identity function against $\all a \to a$:
$$\Gm \Vdash \lam x \Lto \all a \to a$$
Then, two auxiliary variables $a$ and $x$ are introduced to help the type checking:
$$\Gm, a, x:a \Vdash x \Lto a$$
which will be satisfied after several steps, and the worklist becomes
$$\Gm, a, x:a$$
Since the variable declarations $a, x:a$ are only used for a judgment already processed,
they can be safely removed, leaving the remaining worklist $\Gm$ to be further reduced.

@@

The algorithm first analyse the two subtyping judgments and
will find the best solutions $\al = \bt = 1$
(please refer to Figure~\ref{fig:alg} for detailed derivations).
Then we substitute every instance of $\al$ and $\bt$ to $1$,
so the variable declarations can be safely removed from the worklist.
Now we reduce the worklist to the following state
$$\nil \Vdash \blue{(\lam x)~() \To_a a \le 1}, x:1$$
which has a term variable declaration as the top element.
Because no judgments before the declaration refer to $x$,
as a basic property of an ordered context
(Figure~\ref{fig:alg:syntax} shows its well-formedness criteria),
we remove all declarations before the first judgment chain to collect unused variables.
As a result all garbage variables are collected
once the judgment chains refering to them are processed.

>>>>

@@

$$\begin{aligned}
\text{Algorithmic judgement chain}\qquad&\jg &::=&\quad A \le B \mid e\Lto A \mid e\To_{a} \jg \mid \appInfAlg{A}{e}\\
\text{Algorithmic worklist}\qquad&\Gm &::=&\quad \nil \mid \Gm, a \mid \Gm, \al \mid \Gm, x: A \mid \Gm \Vdash \jg\\
\end{aligned}$$

For example, the top judgment of the following worklist
checks the identity function against $\all a \to a$:
$$\Gm \Vdash \lam x \Lto \all a \to a$$
To proceed, two auxiliary variables $a$ and $x$ are introduced to help the type checking:
$$\Gm, a, x:a \Vdash x \Lto a$$
which will be satisfied after several steps, and the worklist becomes
$$\Gm, a, x:a$$
Since the variable declarations $a, x:a$ are only used for a judgment already processed,
they can be safely removed, leaving the remaining worklist $\Gm$ to be further reduced.

Our worklist can be seen as an all-in-one stack,
containing variable declarations and subtyping/typing judgments.
The stack is a enriched form of ordered context,
and it has a similar variable scoping scheme.
The well-formedness condition, shown in Figure~\ref{fig:alg:syntax},
states that every variable must be declared prior to it usage.
Therefore, if any variable declaration is the top element,
then no usage should appear in the rest of the worklist, so it can be removed.

@@

The algorithm first analyse the two subtyping judgments and
will find the best solutions $\al = \bt = 1$
(please refer to Figure~\ref{fig:alg} for detailed derivations).
Then we substitute every instance of $\al$ and $\bt$ to $1$,
so the variable declarations can be safely removed from the worklist.
Now we reduce the worklist to the following state
$$\nil \Vdash \blue{(\lam x)~() \To_a a \le 1}, x:1$$
which has a term variable declaration as the top element.
Because no judgments before the declaration refer to $x$,
as a basic property of an ordered context
(Figure~\ref{fig:alg:syntax} shows its well-formedness criteria),
we remove all declarations before the first judgment chain to collect unused variables.
As a result all garbage variables are collected
once the judgment chains refering to them are processed,
just as what we have mentioned above about the scope tracking.
